When are Fuzzy Extractors Possible?

### 2014-09-30 trunk/info-bounds/FuzzyExtPossibility.tex
reorganizing and cleaning up proof

\paragraph{Our Contribution} We first consider the \emph{distribution-aware} setting.  We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).  Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.  In this work, we consider this minimal goal of a super-logarithmic length key.  If we require a longer output length this increases the requirement on fuzzy min-entropy.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

@@

We then show the situation is worse in the distribution-oblivious setting.  We show that distributional uncertainty is a real drawback to providing security.  We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).  Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).  Under very strong assumptions, computational secure sketches that provide unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.  This negative result is quite strong, it allows the secure sketch to be wrong a $1/4$ of the time and requires the secure sketch to correct a sub constant fraction of errors.

\bnote{add a paragraph here about the negative result for fuzzy extractors}
\bnote{add a paragraph talking about the computational setting}
%The situation is significantly more complicated for distribution-oblivious algorithms.  Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.  However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.

\paragraph{Our approach} \bnote{say something about our methods.  leveled hashing, distributional uncertainty?}
\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  All results are information-theoretic.}
\label{tab:main results}
\end{table}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  Finally, in \secref{sec:dist oblivious} we provide negative results for the distribution-oblivious setting.

@@

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case version of this notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

@@

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  \bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.  The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

@@

\subsection{A necessary condition for security}
\label{sec:minimal conditions}

@@

\section{Distribution-Aware  Sketches}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors) whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.

@@

\begin{table}
\begin{centering}
\begin{tabular}{l | l}
Class of Distribution & Residual entropy achieved by construction\\
\hline
Well-spread distribution & $\Hfuzz(W)$ \\
Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
\end{tabular}
\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.    Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.  Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
\label{tab:upper bounds}
\end{centering}
\end{table}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

@@

\begin{lemma}
\label{lem:flat hashing}
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
\end{corollary}

Note that \consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
\]
For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). The achievable security is proportional to the starting entropy minus the largest number of points in any ball.   Whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).  %That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.  Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.  For a flat distribution, this is also the ball with the largest total weight.  We will see this becomes more difficult as we move to the setting where points have very different probability.  %In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls. We will compensate for this problem by writing down a variable number of bits.
%with a fixed number of neighbors, 
%\begin{align*}
%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
%\end{align*}
%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.

@@

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

@@

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Impossibility of Distribution-Oblivious Secure Sketches}
\label{sec:dist oblivious}

@@

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.  
\end{theorem}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  In this section, we extend this result to fuzzy extractors.  This result has significantly weaker parameters than the previous result but still demonstrates hard.  \bnote{write this}

We begin with the case of perfect correctness in the Hamming metric.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \Theta(2^{n^{1/3}})$ for $t = \Theta(n^{4/5})$. \end{theorem}
\begin{proof}
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance $t=n^{4/5}$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  Let $\nu = n/t = n^{1/5}$.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.

>>>>

\paragraph{Positive Results} We first consider the \emph{distribution-aware} setting.  We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).  Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.  In this work, we consider this minimal goal of a super-logarithmic length key.  If we require a longer output length this increases the requirement on fuzzy min-entropy.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

@@

\paragraph{Negative Results}
We then show the situation is worse in the distribution-oblivious setting.  We show that distributional uncertainty is a real drawback to providing security.  We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).  This result is quite strong, it requires the secure sketch to correct only a constant number of errors and allows the secure sketch to be wrong almost a quarter of the time.

Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).  Under very strong assumptions, computational secure sketches that provide unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

We then show a similar result to fuzzy extractors.  We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).  \thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.  (Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.  Furthermore, the result only applies for fuzzy extractors with perfect correctness.  Many but not all fuzzy extractors have perfect correctness.

Computational fuzzy extractors offer more hope for avoiding the impossibility result.  Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.
%The situation is significantly more complicated for distribution-oblivious algorithms.  Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.  However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.

\paragraph{Our approach} \bnote{say something about our methods?}
\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

@@

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

@@

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\noindent \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

@@

\subsection{Fuzzy min-entropy: necessary for security}
\label{sec:minimal conditions}

@@

\section{Distribution-Aware  Sketches}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors using \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider distributions where points are far apart, distributions where all points have the same probability, and finally arbitrary distributions.

@@

%\begin{table}
%\begin{centering}
%\begin{tabular}{l | l}
%Class of Distribution & Residual entropy achieved by construction\\
%\hline
%Well-spread distribution & $\Hfuzz(W)$ \\
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ \\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$
%\end{tabular}
%\caption{Residual entropy of distribution-aware secure sketches from \secref{sec:distribution aware}.    Here $\delta$ denotes the probability of incorrect reconstruction and $\mathcal{M}$ is the metric space.  Recall that $\Hfuzz(W)$ is an upper bound for the residual entropy.}
%\label{tab:upper bounds}
%\end{centering}
%\end{table}
%\bnote{I'm not convinced this table is useful}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
\end{corollary}

\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n).
$

For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). The achievable security is proportional to the starting entropy minus the largest number of points in any ball.   Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).

@@

Dealing with non-flat distributions requires a new strategy. % The fuzzy extractor must be aware of the density of the current ball.  
Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

@@

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
\label{sec:dist oblivious}

@@

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.  
\end{theorem}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious secure sketch for the elements of $V$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\section{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious fuzzy extractors}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We extend this result to fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).  Obtaining weaker parameters for impossibility of fuzzy extractors makes sense.
\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.
